4d $\cN=1$

### 2019-11-12 4dsusy.tex
merge

The BRST action is
\[
S (\phi, \Bar{\phi}, \psi_\pm) = - \int_{\RR^4} (\d \phi \wedge * \d \Bar{\phi})_R + \int (\psi_+ , \sd \dd \psi_-)_R .
\]

@@

@@

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - \int (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

@@

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
\end{lemma}
\begin{proof}
The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) \\
& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
\end{align*}
The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
\begin{align*}
\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
\end{align*}
Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$, as desired. 
\end{proof}

>>>>

The BRST action is
\[
S (\phi, \Bar{\phi}, \psi_\pm) = \int_{\RR^4}  - (\d \phi \wedge * \d \Bar{\phi})_R + (\psi_+ , \sd \dd \psi_-)_R .
\]

@@

\begin{lem}
\label{lem: oneform}
Let $\alpha$ be any $1$-form on $V$, $\psi \in C^\infty(V, \Sigma)$,  and $Q \in \Sigma$. 
Then
\[
\d (Q, \psi) \wedge * \alpha = * (\rho(\alpha)Q, \sd \dd \psi) .
\]
\end{lem}
\begin{proof}
Let $V_\alpha$ denote the vector field corresponding to $\alpha$. 
Note that $\d(Q,\psi) \wedge * \alpha = * (Q, V_\alpha . \psi)$. 
The result then follows from invariance of $(-,-)$ and the formula $\sd \dd \psi = \rho(\d x_i) (\partial_i \psi)$. 
\end{proof}

@@

The action of the odd part of the $4d$ $\cN=1$ supersymmetry algebra on the $4$-dimensional matter theory is encoded by the following linear and quadratic functionals 
\begin{align*}
I^{(1)}(Q) & = \int \<\phi^*, (Q, \psi_+)\>_R + \<\Bar{\phi}^*, (Q, \psi_-)\>_R + \<\psi_+^*, \rho(\d \phi)Q \>_R +  \<\psi_-^*, \rho(\d \Bar{\phi})Q \>_R \\
I^{(2)}  (Q_1 \otimes Q_2) & = \int \frac{1}{2}(\Gamma(Q_1, Q_2), \Gamma(\psi_+^*, \psi_-^*)) - (Q_1, \psi_+^*)(Q_2, \psi_-^*) - \int (Q_2, \psi_+^*)(Q_1, \psi_-^*) 
\end{align*}
for $Q, Q_1, Q_2 \in S_+ \oplus S_-$

@@

\begin{lemma} 
One has $\{S, I^{(1)}\} (Q) = 0$ for all $Q \in S_+ + S_-$. 
\end{lemma}
\begin{proof}
The BV bracket involving terms in $S$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
- \left\{\d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\}  (Q) & = \d (Q, \psi_+) \wedge * \d \Bar{\phi} + \d \phi \wedge * \d (Q_-, \psi_-) 
%\\
%& = \Gamma(\sd \dd \psi_+, Q) \wedge * \d \Bar{\phi} \pm \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q_-) .
\end{align*}
The BV bracket involving terms in $S$ depending on $\psi_\pm$ is:
\begin{align*}
\left\{ (\psi_+ , \sd \dd \psi_-) \; , \; I^{(1)} \right\} (Q) & = (\rho(\d \phi) Q, \sd \dd \psi_-) + (\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q)) \\ & =  (\rho(\d \phi) Q, \sd \dd \psi_-) - (\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q) \\ & = \d \phi \wedge * \Gamma(\sd \dd \psi_-, Q) - \d \Bar{\phi} \wedge * \Gamma(\sd \dd \psi_+, Q)
\end{align*}
Adding the two terms up, we see that $\{S,I^{(1)}\}(Q) = 0$ by Lemma \ref{lem: oneform} as desired. 
\end{proof}
